K2 Analysis

### 2013-06-22 text/micha_stat_analysis/notes.tex
stat notes sec com

@@

The factor \textsc{Position} cannot be dropped without dramatically
reducing explanatory power of the model. However, if we abstract over
intonation and conditions, we get the following table:
\begin{center}
\centering
\begin{tabular}{rrrr}
  & \emph{lc} & \emph{ec} & \emph{false} \\ 
  \midrule
  Pos 1 & 144 & 49 & 29 \\ 
  Pos 2 & 148 & 48 & 26 \\ 
  Pos 3 & 150 & 48 & 20 \\ 
  Pos 4 &  70 & 37 & 13 \\ 
\end{tabular}
\end{center}
There is no interaction between \textsc{Position} and
\textsc{Response} ($\chi^2$, $df=6$, $p=0.3798$), suggesting that
\textsc{Position} does not affect the overal distribution of readings.

>>>>

\todo[inline]{is this convincing enough to dispense with any potential
doubt about interferences from our screwed up block design?}

@@

The factor \textsc{Position} cannot be dropped without dramatically
reducing explanatory power of the model. However, inspecting the
coefficients of the above model, we see that the only role of factor
\textsc{Position} is to account for the relatively fewer data points
at position four. Moreover, if we abstract over intonation and
conditions, we get the following table:
\begin{center}
\centering
\begin{tabular}{rrrr}
  & \emph{lc} & \emph{ec} & \emph{false} \\ 
  \midrule
  Pos 1 & 144 & 49 & 29 \\ 
  Pos 2 & 148 & 48 & 26 \\ 
  Pos 3 & 150 & 48 & 20 \\ 
  Pos 4 &  70 & 37 & 13 \\ 
\end{tabular}
\end{center}
There is no interaction between \textsc{Position} and
\textsc{Response} ($\chi^2$, $df=6$, $p=0.3798$), suggesting that
\textsc{Position} does not affect the overal distribution of readings.

\todo[inline]{is this convincing to cast away \textsc{Position}
  effects? do we really need to care in this case? there is no
  particularly obvious difference across positions that one would need
  to worry about; also the way conditions were presented in the second
  block don't really lead to any obvious pattern either; in other
  words, neither does the faulty design suggest a positional pattern
  (or at least I can conceive of one), nor does there seem to be one
  (or at least I don't see one) }
